On the properties of projectile motion and quadratic air resistance

### 2016-03-17 Paper/main.tex
minor
Minor
Thicker lines for print

	\section{Introduction}
	Projectile motion is the motion in which an object travels under the constant effect of a force field. The simplest form of projectile motion considers a closed system with no air resistance while a more advanced one might consider multiple gravitational pulls or air resistance. This paper will first describe the ideal trajectory and properties of a projectile parabola and then develop and test an analytical solution to quadratic air resistance.
	\section{Trajectory}
	Consider a Euclidean space $\mathbb{R}^3$ with the three axes $x \comma y$ and $z$. At any time $t$ we want to be able to describe the acceleration, velocity and position of an object with the three vectors $A = (a_x \comma a_y \comma a_z)\comma V = (v_x \comma v_y \comma v_z)$ and $P = (x \comma y \comma z)$. Let $\theta$ be the angle between the $xz$ plane and the initial direction of the object and $\alpha$ the angle between the $x$ axis and a projection of the path on the $xz$ plane. This is visualized in the graph below.
	\begin{center}
		\trimbox{0cm 0cm 0cm -0.6cm} {
			\tdplotsetmaincoords{40}{120} 
			\begin{tikzpicture} [scale = 4, tdplot_main_coords, axis/.style={ -> , black, semithick}, 
			vector/.style={-stealth, black, ultra thick}, 
			vector guide/.style={dashed, black, thick}]

@@

	Solving $\frac{\partial d}{\partial \theta} = 0$ gives the maxima of $R$

@@

	We let $C = 0$ since $v(0) = 0$ meaning $T = t$. We can now find $y$ as it is the antiderivative of $v$.

@@

@@

	We can plot another $y(t)$ where $k$ is much smaller which should result in our object not reaching its terminal velocity in such short time. The following measurements are from a small steel ball with $k = 0.00313$.
	\begin{align}\nonumber
		\begin{cases}\nonumber
			C_D &= 0.47 \\
			m &= 0.022\,kg\\
			y_0 &= 3\,m\\
			v_0 &= 0\,m/s\\
			\rho &= 1.225\,kg/m^3\\
			A &= 0.00023916\,m^2
		\end{cases}
	\end{align}
	\begin{center}
		\begin{tikzpicture}
		\begin{axis}[ xlabel=t (s), ylabel=y (m)]
		\addplot[solid] coordinates {(0.000, 3.000) (0.010, 3.000) (0.020, 2.998) (0.030, 2.996) (0.040, 2.992) (0.050, 2.988) (0.060, 2.982) (0.070, 2.976) (0.080, 2.969) (0.090, 2.960) (0.100, 2.951) (0.110, 2.941) (0.120, 2.929) (0.130, 2.917) (0.140, 2.904) (0.150, 2.890) (0.160, 2.874) (0.170, 2.858) (0.180, 2.841) (0.190, 2.823) (0.200, 2.804) (0.210, 2.784) (0.220, 2.762) (0.230, 2.740) (0.240, 2.717) (0.250, 2.693) (0.260, 2.668) (0.270, 2.642) (0.280, 2.615) (0.290, 2.587) (0.300, 2.558) (0.310, 2.528) (0.320, 2.497) (0.330, 2.466) (0.340, 2.433) (0.350, 2.399) (0.360, 2.364) (0.370, 2.328) (0.380, 2.292) (0.390, 2.254) (0.400, 2.215) (0.410, 2.175) (0.420, 2.135) (0.430, 2.093) (0.440, 2.050) (0.450, 2.007) (0.460, 1.962) (0.470, 1.917) (0.480, 1.870) (0.490, 1.823) (0.500, 1.774) (0.510, 1.725) (0.520, 1.674) (0.530, 1.623) (0.540, 1.570) (0.550, 1.517) (0.560, 1.463) (0.570, 1.407) (0.580, 1.351) (0.590, 1.294) (0.600, 1.236) (0.610, 1.176) (0.620, 1.116) (0.630, 1.055) (0.640, 0.993) (0.650, 0.930) (0.660, 0.866) (0.670, 0.801) (0.680, 0.735) (0.690, 0.668) (0.700, 0.600) (0.710, 0.531) (0.720, 0.461) (0.730, 0.391) (0.740, 0.319) (0.750, 0.246) (0.760, 0.172) (0.770, 0.098) (0.780, 0.022) (0.790, -0.055) };

>>>>

	\section{Introduction}
	Projectile motion is the motion in which an object travels under the constant effect of a force field. The simplest form of projectile motion considers a closed system with no air resistance while a more advanced one might consider multiple gravitational pulls or air resistance. This paper will first describe the ideal trajectory and properties of a projectile parabola and then develop and test an analytical solution to quadratic air resistance.
	\section{Trajectory}
	Consider a Euclidean space $\mathbb{R}^3$ with the three axes $x \comma y$ and $z$. At any time $t$ we want to be able to describe the acceleration, velocity and position of an object with the three vectors $A = (a_x \comma a_y \comma a_z)\comma V = (v_x \comma v_y \comma v_z)$ and $P = (x \comma y \comma z)$. Let $\theta$ be the angle between the $xz$ plane and the initial direction of the object and $\alpha$ the angle between the $x$ axis and a projection of the path on the $xz$ plane. This is visualized in the graph below.
	\begin{center}
		\trimbox{0cm 0cm 0cm -0.6cm} {
			\tdplotsetmaincoords{40}{120} 
			\begin{tikzpicture} [scale = 4, tdplot_main_coords, axis/.style={ -> , black, semithick}, 
			vector/.style={-stealth, black, ultra thick}, 
			vector guide/.style={dashed, black, ultra thick}]

@@

	Solving $\frac{\partial d}{\partial \theta} = 0$ gives the maxima of $R$.

@@

	$v(0) = 0$ implies $C = 0$ meaning $T = t$. We can now find $y$ as it is the antiderivative of $v$.

@@

		\end{cases} \implies k = 0.432

@@

	We can plot another $y(t)$ where $k$ is much smaller which should result in our object not reaching its terminal velocity in such short time. The following measurements are from a small steel ball with $k = 0.00313$.
	\begin{align}\nonumber
		\begin{cases}\nonumber
			C_D &= 0.47 \\
			m &= 0.022\,kg\\
			y_0 &= 3\,m\\
			v_0 &= 0\,m/s\\
			\rho &= 1.225\,kg/m^3\\
			A &= 0.00023916\,m^2
		\end{cases} \implies k = 0.00313
	\end{align}
	\begin{center}
		\begin{tikzpicture}
		\begin{axis}[ xlabel=t (s), ylabel=y (m)]
		\addplot[solid] coordinates {(0.000, 3.000) (0.010, 3.000) (0.020, 2.998) (0.030, 2.996) (0.040, 2.992) (0.050, 2.988) (0.060, 2.982) (0.070, 2.976) (0.080, 2.969) (0.090, 2.960) (0.100, 2.951) (0.110, 2.941) (0.120, 2.929) (0.130, 2.917) (0.140, 2.904) (0.150, 2.890) (0.160, 2.874) (0.170, 2.858) (0.180, 2.841) (0.190, 2.823) (0.200, 2.804) (0.210, 2.784) (0.220, 2.762) (0.230, 2.740) (0.240, 2.717) (0.250, 2.693) (0.260, 2.668) (0.270, 2.642) (0.280, 2.615) (0.290, 2.587) (0.300, 2.558) (0.310, 2.528) (0.320, 2.497) (0.330, 2.466) (0.340, 2.433) (0.350, 2.399) (0.360, 2.364) (0.370, 2.328) (0.380, 2.292) (0.390, 2.254) (0.400, 2.215) (0.410, 2.175) (0.420, 2.135) (0.430, 2.093) (0.440, 2.050) (0.450, 2.007) (0.460, 1.962) (0.470, 1.917) (0.480, 1.870) (0.490, 1.823) (0.500, 1.774) (0.510, 1.725) (0.520, 1.674) (0.530, 1.623) (0.540, 1.570) (0.550, 1.517) (0.560, 1.463) (0.570, 1.407) (0.580, 1.351) (0.590, 1.294) (0.600, 1.236) (0.610, 1.176) (0.620, 1.116) (0.630, 1.055) (0.640, 0.993) (0.650, 0.930) (0.660, 0.866) (0.670, 0.801) (0.680, 0.735) (0.690, 0.668) (0.700, 0.600) (0.710, 0.531) (0.720, 0.461) (0.730, 0.391) (0.740, 0.319) (0.750, 0.246) (0.760, 0.172) (0.770, 0.098) (0.780, 0.022) (0.790, -0.055) };
